Figures

### 2018-07-12 figures/07_cor_mat_hmap.Rmd
add correlation values to hmap fig

```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}

>>>>

```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=4, fig.height=3.7, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}

### 2018-07-12 manuscript/figures.Rmd
add correlation values to hmap fig

```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
```

>>>>

```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
```
